\thesistitle

### 2019-07-18 sections/clonerefactor.tex
Fixed formulas

\begin{equation}\label{eq:variabilityclonerefactor}
\frac{|\{x>0 \and y>0 \and x \neq y | x \in E_1 \union E_2, y \in E_3 \union E_4\}|}{(s_1+s_2)+(s_3+s_4)}*100
\end{equation}

@@

\begin{equation}\label{eq:t2rcloneequality}
E_1\text{ is cloned with }E_2\text{ iff }|E_1|=|E_2| \and \forall {x<0 \Rightarrow x=y | x \in E_1, y \in E_2}
\end{equation}

>>>>

\begin{equation}\label{eq:variabilityclonerefactor}
\frac{|\{x>0 \land y>0 \land x \neq y\text{ }|\text{ }x \in E_1 \cup E_2, y \in E_3 \cup E_4\}|}{(s_1+s_2)+(s_3+s_4)}*100
\end{equation}

@@

\begin{equation}\label{eq:t2rcloneequality}
E_1\text{ is cloned with }E_2\text{ iff }|E_1|=|E_2| \land \forall {x<0 \Rightarrow x=y | x \in E_1, y \in E_2}
\end{equation}
